Visualizing Contingency Tables

### 2006-10-27 trunk/vcd/paper/Handbook/hsc.Rnw
fixed Figure 9 (used wrong HCL palette)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@616 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}
\begin{center}
<<diverging,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
par(mfrow = c(1,1), mar = c(1,1,1,1), oma = c(0,0,0,0))
plot.new()
rect(0:4/5, 0.2, 1:5/5, 0.5, border = 0, col = diverge_hcl(5))
rect(0, 0.2, 1, 0.5, border = 1, col = NULL)
rect(0:4/5, 0.55, 1:5/5, 0.85, border = 0, col = diverge_hsv(5))
rect(0, 0.55, 1, 0.85, border = 1, col = NULL)
text(c(1:5/5 - 0.1), 0.11, c("(260, 100, 50)", "(260, 50, 70)", "(H, 0, 90)", "(0, 50, 70)", "(0, 100, 50)"))
text(c(1:5/5 - 0.1), 0.91, c("(240, 100, 100)", "(240, 50, 100)", "(H, 0, 100)", "(0, 50, 100)","(0, 100, 100)"))
@ 
\caption{Diverging color palettes for the HSV space (upper part) and
  the HCL space (lower part), ranging from blue over a neutral color to
  red. The triples indicate the settings for 
  the three dimensions: (Hue, Saturation, Value)
  in the upper part, and (Hue, Chroma, Luminance) in the lower part.
  In a monochrome version of the paper, the right and left hand
  sides of the HCL colors palette appear identical. }
\label{fig:diverging}
\end{center}
\end{figure}

>>>>

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}
\begin{center}
<<diverging,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
par(mfrow = c(1,1), mar = c(1,1,1,1), oma = c(0,0,0,0))
plot.new()
rect(0:4/5, 0.2, 1:5/5, 0.5, border = 0, col = diverge_hcl(5, c = 100, l = c(50, 90)))
rect(0, 0.2, 1, 0.5, border = 1, col = NULL)
rect(0:4/5, 0.55, 1:5/5, 0.85, border = 0, col = diverge_hsv(5))
rect(0, 0.55, 1, 0.85, border = 1, col = NULL)
text(c(1:5/5 - 0.1), 0.11, c("(260, 100, 50)", "(260, 50, 70)", "(H, 0, 90)", "(0, 50, 70)", "(0, 100, 50)"))
text(c(1:5/5 - 0.1), 0.91, c("(240, 100, 100)", "(240, 50, 100)", "(H, 0, 100)", "(0, 50, 100)","(0, 100, 100)"))
@ 
\caption{Diverging color palettes for the HSV space (upper part) and
  the HCL space (lower part), ranging from blue over a neutral color to
  red. The triples indicate the settings for 
  the three dimensions: (Hue, Saturation, Value)
  in the upper part, and (Hue, Chroma, Luminance) in the lower part.
  In a monochrome version of the paper, the right and left hand
  sides of the HCL colors palette appear identical. }
\label{fig:diverging}
\end{center}
\end{figure}
